---
title: "Introduction.Rmd"
author: "Cameron Mandley"
date: "5/3/2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(Workout3-Cameron-Mandley.R)
```

## Binomial

`"binomial"` is a package 
that simulates variations of binomial distributions.



## Creating a `binomial variable`

Create a `"Binomial Variable"` object with the function `bin_variable()`:

```{r}
#Creates an object of type binvar
bin1 <- bin_variable(trials = 10, p = 0.3)
```
You can change the arguments `trials` and `p`

## Printing a Summary of your binomial variable

Once you have created your binomial variable, you can create a summary of it and print it out
```{r}
#Creates a summary of the object
binsum1 <- summary(bin1)
```

## Plot of relative frequencies

You can use the function `plot()` to create a graohic of your binomial distribution object:
```{r}
plot.bindist(binsum1)
plot.bincum(binsum1)
```

